---
title: "Regression Model of the 'mtcars' data"
author: "Julian Jang"
date: "November 19th, 2015"
output: html_document
---
___
### Summary
 This analysis was performed for the 'mtcars' dataset. By looking at a data set of a collection of cars, I was interested in exploring the relationship between a set of variables and MPG(miles per gallon) as outcome. I was particularly interested to explore.

  * 'Is an automatic or manual transmission better for MPG'
  * 'Quantify the MPG difference between automatic and manual transmissions'

 In order to figure out the answers of these questions, I have performed exploratory data analysis, and used hypothesis test and linear regression as methodologies to make inference.
 
___
### Explanations of variables
 At first, I have looked the meaning of 'mtcars' dataset variables over help pages by the command '?mtcars'. The meanings of the variables are below.

|column No.|Variable Name|Explanation|
|:--:|:--:|:--:|
|[, 1]|mpg|Miles/(US) gallon|
|[, 2]|cyl|Number of cylinders|
|[, 3]|disp|Displacement (cu.in.)|
|[, 4]|hp|Gross horsepower|
|[, 5]|drat|Rear axle ratio|
|[, 6]|wt|Weight (lb/1000)|
|[, 7]|qsec|1/4 mile time|
|[, 8]|vs|V/S|
|[, 9]|am|Transmission (0 = automatic, 1 = manual)|
|[,10]|gear|Number of forward gears|
|[,11]|carb|Number of carburetors|

 I found out that 'mpg' might be used as the response variable and the 'am(transmission)' is the factor variable.

___
### EDA for 'mtcars' dataset.
 I've started the analysis by performing initial exploratory data analysis(EDA) to get a better idea of the existing patterns between variables in the data set. Below is that I created pairwise scatter plots. This is a nice way to investigate the relationship between all the variables in this data set. And, I also created histograms of 'mpg' according to am type.

```{r, fig.align = 'center'}
pairs(mtcars, panel = panel.smooth, main="Pair Graph of Motor Trend Car Road Tests")
par(mfrow = c(1, 2), mar=c(3.1, 3.1, 1.1, 2.1))
hist(mtcars$mpg[mtcars$am == 0], col = "pink", main = "MPG with Automatic(am=0)")
boxplot(mtcars$mpg[mtcars$am == 0], horizontal=T,  outline=T, frame=F, col = "royalblue", add = T)
hist(mtcars$mpg[mtcars$am == 1], col = "pink", main = "MPG with Manual(am=1)")
boxplot(mtcars$mpg[mtcars$am == 1], horizontal=T,  outline=T, frame=F, col = "royalblue", add = T)
```

 Also, I have compared the average of 'mpg' between 'Automatic' and 'Manual'. The result of it showed me They have difference of average. So, I needed to analyze by t.test.

```{r}
with(mtcars, tapply(mpg, am, mean))
```

___
###Statistical Inference(t test)
 I have performed the t.test with my hypothesises below.

  * Null hypothesis(HO): The 'mpg' is not different according to type of 'transmission'.
  * Alternative hypothesis(H1): The 'mpg' is different according to type of 'transmission'.

```{r}
with(mtcars, t.test(mpg ~ am))
```

 The result of 't.test' show me that the 'p-value' is '0.0014' in 95% confidence interval. So the two groups are not same each other.

___
### Regression Model
#### 1. Regression modeling with only the 'am' variable

```{r}
mtcars$am <- factor(mtcars$am)
summary(lm(mpg ~ am, data = mtcars))
```

 The coefficents of the result is '0.0003' of 'am' factor and '1.13e-15' of a intercept. And, 'p-value' is '0.0003' but the adjusted R^2 is '0.3385'. So, I can say that the realation of the variables between 'mpg' and 'am' are meaningful. But, this model is not enough to explain the relations between 'mpg' and other variables.

#### 2-1. Regression modeling with the stepwise method
 I have performed regression modelling with all variales by stepwise method.

```{r}
summary(step(lm(mpg ~ ., data = mtcars), trace = 0, steps = 10000))
```

 The 'p-value' and the adjusted R^2 was each '1.21e-11' and '0.8336'. I think this model is nice. And, I have looked over the conefficients of the variables. Among five variables, only 'wt' and 'qsec' have significant meaning in 99% confidence interval. And, the coefficients of 'wt' and 'qsec' are '-3.9165' and '1.2259'.

___
### Conclusion
This model is "mpg = wt + qsec + am". The Adjusted R-squared value is 0.8336. And, all of the coefficients are significant at 0.05 significant level. Then, I have tried the ‘Residual Diagnostics’, the result is that residuals are met with the normal distribution, the independence, the random distribution and no outliers.

___
### Appendix

```{r, fig.align = 'center'}
par(mfrow = c(2, 2))
plot(step(lm(mpg ~ ., data = mtcars), trace = 0, steps = 10000))
```