---
title: "Analysis_Toothgrowth"
author: "Julian Jang"
date: "October 25, 2015"
output: html_document
---
Analysis of Toothgrowth dataset
---
### Overview(Summary)
#### The explanation of 'Toothgrowth' dataset is below. This dataset is a data show that the effect of Vitamin C on Tooth Growth in Guinea Pigs. The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).
 - len : numeric value for Tooth length
 - supp : factor value for Supplement type (VC or OJ).
 - dose : numeric value for Dose in milligrams.

### Basic EDA
I looked through the dataset with boxplots. I made boxplots to find out the difference of length through supplement methods and amount of dosage. The results are below. I glanced, I think that the difference existed in each control group.

```{r, echo = TRUE}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
par(mfrow = c(2, 1))
plot(len ~ supp, data = ToothGrowth, main = "Comparison between 'Orange Juice' and 'Vitamin C'")
plot(len ~ dose, data = ToothGrowth, main = "Comparison of amount of dose")

with(ToothGrowth, tapply(len, supp, mean))
with(ToothGrowth, tapply(len, dose, mean))
```

### t test for groups which are divied accordingly supplement method.
I divided the dataset into two parts-'VC' and 'OJ'. I used two external packages('tidyr', 'dplyr'). And, I t tested. The result of t test is that No difference between 'VC' and 'OJ'. The p-value is '0.06063'. So, I can't deny Null hypothesis because that my p-value is greater than 0.05 I can't deny Null hypothesis.

```{r, echo = TRUE, message = FALSE}
if (!require(tidyr)) { install.packages("tidyr") }
if (!require(dplyr)) { install.packages("dplyr") }

Supp.df <- ToothGrowth %>% select(supp, len) %>% spread(supp, len)
with(Supp.df, t.test(VC, OJ))
```

### t test for comparison among the amount of dose.
I executed t.test to compare difference of length by amount of dose in same way. I tested 3 times for 3 groups. In summary, The length was different according to amount of dose. '0.5 & 1.0', '0.5 & 2.0' and '1.0 & 2.0' were all different in mean value. The results of t tests are below.

```{r, echo = TRUE, message = FALSE}
Dose.df <- ToothGrowth %>% select(dose, len) %>% spread(dose, len)
names(Dose.df) <- c("a_0.5", "a_1", "a_2")

Dose.t_1 <- with(Dose.df, t.test(a_0.5, a_1))
Dose.t_1$p.value
Dose.t_1$conf.int

Dose.t_2 <- with(Dose.df, t.test(a_0.5, a_2))
Dose.t_2$p.value
Dose.t_2$conf.int

Dose.t_3 <- with(Dose.df, t.test(a_1, a_2))
Dose.t_3$p.value
Dose.t_3$conf.int
```

### Conclusion
 - Null Hypothesis: The length of tooth will have no diffrence according to dose method and amount of Vitamin C.
 - Alternative Hypothesis: The length of tooth will diffrent according to dose method and amount of Vitamin C.

The result of test.

 - No difference on dose methods.
 - Amount of dose causes difference of length of tooth.

